eu-circle_case-study-1

### 2016-10-17 EU-Circle/eu-circle_case-study-3.Rmd
Added DS scripts for temperature

```{r trend-map}
triangle <- subset(Z,is=c(2,3,7))
## The stations are not situated quite where there is valid slp data in the EOBS dataset
## It's only their coordinates that is used for interpolating SLP for three stations
## Using station objects as is-object makes the results a station object
attr(triangle,'longitude') <- c(-4,-2,-1.25)
attr(triangle,'latitude') <- c(50.50,51,49)
pp.eobs <- regrid(slp.eobs,is=triangle)
## Use triagulation for stations to estimate the wind
uv <- geostrophicwind(pp.eobs)
plot(annual(uv,nmin=300),main='zonal and meridional wind components',
     sub='Estimated from triangulation of mean sea-level pressure from EOBS')
```

>>>>

```{r trend-map}
## Fudge it - pick some windstations, but do not use their data. Reset the
## coordinates to select a triangle of SLP from the EOBS data.
ss <- select.station(param='slp',src='ecad',cntr=c('France','UNITED KINGDOM'))
fx <- station(ss)
triangle <- subset(fx,is=1:3)
## The stations are not situated quite where there is valid slp data in the EOBS dataset
## It's only their coordinates that is used for interpolating SLP for three stations
## Using station objects as is-object makes the results a station object
attr(triangle,'longitude') <- c(-4,-2,-1.25)
attr(triangle,'latitude') <- c(50.50,51,49)
pp.eobs <- regrid(slp.eobs,is=triangle)
## Use triagulation for stations to estimate the wind
uv <- geostrophicwind(pp.eobs)
plot(annual(uv,nmin=300),main='zonal and meridional wind components',
     sub='Estimated from triangulation of mean sea-level pressure from EOBS',zoom=7)
```
